Alleviating the Topology Mismatch Problem in Unstructured and Structured P2P Overlay Networks: A Survey

### 2014-01-23 structured.tex
2012.08.20 (Vassilis) Added LaTeX tables (known issue on wrapping text inside cells). Reshaped discussion material. Introducing rough, algorithm performance, estimation (high, medium, low) by tracking efficiency, control overhead and scalability. First attempt on plotting data in a systematic way (needs more work though).

@@

After finding its first neighbour, the newcomming peer is assigned an ID using
information gathered during the iterative neighbour selection phase. Virtual
coordinates are assigned to the newcomming peer by using the distances of two
closest nodes and their neighbours, so that Euclidean distances between the node
and all known hosts predict the network latency between
them\cite{cox_vivaldi_2004}. The benefit of these synthetic coordinates are that
they are explicitly used as the node's ID, and distance computations among nodes
can be done in ID space without requiring physical measurements.

@@

One major limitation of \textit{Mithos} is that the protocol cannot handle
dynamic arrivals and removals from the network, as is happens in mobile
networks.

@@

@@

@@

@@

@@

%
% TODO: SOME DISCUSSION
%
%The use of Traceroute as a tool for implementing the distance measuring
%infrastructure raise concearns about its efficiency and scalability. Being,
%primarilly, a network diagnostic utility, it is concearned too heavy weighted
%and intrucive for use in a larger scale\cite{ratnasamy_binning_2002}.
%Additionally, disabling ICMP is a common administrative policy for edge sites
%to enforce security, while dumping BGP routing
%tables\cite{krishnamurthy_bgpclust_2000} is not directly available to the
%application layer.
% Even though traceroute provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PChord}
\emph{PChord}\cite{hong_pchord_2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. Due to the fact that,
with each step, there is always progress towards the target node in the ID
space, PChord will result in a reduced hop number than Chord, since each hop in
PChord is larger or at least equal in the key space. Passing through proximity
links in the underlaying network means reduced routing cost. Additionally, if
the number of entries in the proximity list is the same as the number of network
partitions, PChord prevents hops from jumping in and out the network partition
the current node belongs to.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Chord6}
\emph{Chord6} \cite{xiong_chord6_2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces interdomain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

%
% TODO: SOME DISCUSSION
% However, even though nodes in the same domain would have close identifiers,
% nodes in two close domains may have very different ones.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{sun_quasi_2008}
confronts the topology mismatch problem, in the Chord DHT context which, in its
vanilla version, takes no consiteration for the underlying physical network
topology during the construction of the identifier cycle. To construct a
\emph{Quasi-Chord} network three steps are followed needed. First, each host
acquires its coordinates in the geometric space utilizing the \emph{global
network position (GNP)} protocol \cite{ng_gnp_2001}. Second, using the
\emph{Cantor space filling curve}, the $2$-dimensional space is converted to a
$1$-dimensional one, used in the last, third, step to build the Quasi-Chord
circle according to the host's Cantor value.

@@

@@

@@

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion on the Algorithms for Structured Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}[h!]
\hspace{-3ex}
\begin{center}
\footnotesize
%\begin{landscape}
\begin{longtable}{
|>{\columncolor[gray]{.7}}m{0.2\columnwidth}
|>{\columncolor[gray]{.9}}m{0.4\columnwidth}
|>{\columncolor[gray]{.8}}m{0.2\columnwidth}
|>{\columncolor[gray]{.9}}m{0.2\columnwidth}
%|>{\columncolor[gray]{.9}}m{0.1\columnwidth}
%|>{\columncolor[gray]{.8}}m{0.1\columnwidth}
%|>{\columncolor[gray]{.9}}m{0.1\columnwidth}
%|>{\columncolor[gray]{.8}}m{0.1\columnwidth}
|}
\caption{Decentralized Structured Algorithms}\label{fig:struct_compare_table}\\
\hline
\rowcolor[gray]{.5}
\textbf{Algorithm} & \textbf{Overlay structure} & \textbf{Base protocol} & \textbf{Scalability} \\
\hline
\endfirsthead
\multicolumn{4}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\rowcolor[gray]{.5}
\textbf{Algorithm} & \textbf{Overlay structure} & \textbf{Base protocol} & \textbf{Scalability} \\
\hline
\endhead
\hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot

\hline
\textbf{Global Softstate} &
\textbf{Geographic layout} Uses first landmark clustering
then measures RTTs to identify close nodes &  &  \\

\hline
\textbf{Mithos} &
\textbf{Geographic layout} Uses nodes as topology landmarks and directed
incremental probing to optimize topology & & Scales well as all
operations are local ??? \\

\hline
\textbf{Self-Adaptive Topology Matching} &
\textbf{Proximity neighbour selection} Uses lightweight probing and
selective jumps to optimize the topology & CAN &  Better than Mithos \\

\hline
\textbf{Delay Aware P2P System} & \textbf{} & & \\

\hline
\textbf{VERSION OF CHORD - DHT-PNS} &
\textbf{Proximity neighbour selection} Uses Proximity Neighbour Selection and the Vivaldi
system & Chord  &  \\

\hline
\textbf{MAY OMIT- VERSION OF CHORD - Quasi-Chord} &
\textbf{Proximity based}  & Chord  &  \\

\hline
\textbf{LAPTOP} &
\textbf{Geographic layout} Hierarchical overlay structure  &  & routing path length $\log{_d N}$,
join/leave overhead $d\log{_d N}$ \\

\hline
\textbf{IP-Based Clustering} &
\textbf{Proximity neighbour selection} Proximity neighbour selection based on longest common
prefix of IP addresses &    &  \\

\hline
\textbf{CHOord considering Proximity on IPv6} &
\textbf{Proximity routing} Uses IPv6 address format to provide proximity &  Chord
 & Better than Chord \\

\hline
\textbf{Proximity in Kademlia} &
\textbf{Proximity routing} Applies  proximity neighbour selection (PNS) and proximity route selection (PRS)
to Kademlia & Kademlia &   \\

\hline
\textbf{Cone} &
\textbf{Proximity neighbour selection} Uses proximity neighbour selection (PNS) & Chord  & Better than Chord \\

\hline
\textbf{DynaMO} &  &  &  \\

\hline
\textbf{MAY OMIT-BADLY WRITTEN-PChord} &
\textbf{Proximity based}  &  Chord  & \\

\hline
\textbf{AChord} &  & & \\

\hline
\textbf{Chord6} &
\textbf{Proximity routing} Uses IPv6 hierarchical address format to cluster
topologically close nodes & Chord  &  \\

\hline
\end{longtable}
%\end{landscape}
\end{center}
\vspace{-2.5ex}
\vspace{-2.5ex}
%\label{fig:struct_compare_table}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Geographic Layout} \label{section:geographic_layout}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: TAKEN FROM ALGORITHMS SUBSECTION. SHOULD BE MERGED WITH DISCUSSION

Inside geographic layout category fall those kind of methods which practically
position physically close by nodes together in the application space as well.
This is done by adjusting and maintaining the routing tables of all involved
peers accordingly by exploiting proximity information that describe the overall
geographic positioning of the peer nodes. One popular method for detecting and
constructing a geographic view of the underlying network is the use of well
established servers dedicated to landmarking the physical space, pretty much as
discussed in Section \ref{sec:landmark} of landmark based proximity in the
unstructured P2P networks. The same disadvantages of difficult and inaccurate
positioning and the cost of deploying and maintaining these landmarks apply in
this case as well.
% TODO: maybe a discussion sentence bellow
Even though managing the overlay structure based on the geographic layout of the
nodes improves the query efficiency of the system, on the other hand, it tends
to create hotspots, and the needed failure resilience is undermined by the fact
that close by nodes are more likely to suffer collective failures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: Geographic Layout
%
%\begin{itemize}
% \item Geographic Layout\\
%The node IDs are assigned in such a way that nodes close by in the physical
%network topology, be close in the node ID space as well. Implementations that
%work relatively well with this approach have been incorporated into CAN. Nodes
%measure the RTT between themselves and a set of landmarks in order to match the
%CAN space as much as possible to the physical one. Unfortunately, the approach
%requires well known landmark servers and for that matter is  not fully
%self-organizing which can further lead to imbalanced node distribution. On
%other DHTs, such as Chord or Pastry, another problem emerges.  To gain fault
%tolerant properties, these protocols, replicate key-value pairs on neighbouring
%(in the ID space) nodes. When a proximity-based node ID assignment has been
%used, the needed failure resilience is undermined by the fact that close by
%nodes are more likely to suffer collective failures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proximity Routing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: TAKEN FROM ALGORITHMS SUBSECTION. SHOULD BE MERGED WITH DISCUSSION

Proximity routing does not require routing tables to be built using any
knowledge about network proximity. On the other hand it exploits such knowledge
in order to choose the best next hop during routing a message. This approach
balances between choosing the node that will further progress the routing
towards the destination and choosing the closest entry in the routing table, in
terms of network proximity.
% TODO: looks like discussion material
Thus, it is relatively less effective than
geographical layout when applied to CAN(-like) implementations. Moreover, the
technique has been incorporated into a version of Chord causing an increase on
the overhead of node joins and the size as well as maintenance cost of finger
tables.

% Moreover, the technique has been incorporated into a version of Chord
% (TODO: PChord | additionally check whether this is true) causing an increase
% on the overhead of node joins and the size as well as maintenance cost of
% finger tables.

%
%\cite{dabek_cfs_2001} proposes a server selection scheme for the Chord DHT, on
%the domain of proximity routing selection. In \emph{CFS}, each node predicts
%the entire lookup latency as a function of the total number of nodes and the
%average overlay next routing peer. The problem is that it is very difficult to
%have a clear picture on the total number of nodes and the average hop latency
%from the local. This leads to rough estimations that consequently decreases
%overall performance.
%
The methods that use proximity routing and their details are listed below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proximity Neighbour Selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: TAKEN FROM ALGORITHMS SUBSECTION. SHOULD BE MERGED WITH DISCUSSION

\emph{Proximity Neighbour Selection} constructs the routing tables using
proximity knowledge. The proximity information used in this method is different
than the landmark based systems described in
Section~\ref{section:geographic_layout}, as time-to-live values between nodes,
or directly node ID prefixes are used to detect proximity. Tapestry, Pastry, and
CAN successfully implemented the proximity into their algorithms by using this
approach. The routing protocol in Pastry is based on longest node ID prefix
matching, while CAN uses RTT values to detect close by nodes.
\cite{castro_proximityp2p_2002} reports that proximity neighbour selection as an
effective proximity based method. Proximity Neighbor Selection based algorithms
are described in detail below.

>>>>

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximatelly 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sucrificing the the decentralised nature of DHTs and
% thus poorly scalling.
low
\end{tabular}
\end{center}

@@

After finding its first neighbour, the newcomming peer is assigned an ID using
information gathered during the iterative neighbour selection phase. Virtual
coordinates are assigned to the newcomming peer by using the distances of two
closest nodes and their neighbours, so that Euclidean distances between the node
and all known hosts predict the network latency between them
\cite{cox_vivaldi_2004}. The benefit of these synthetic coordinates are that
they are explicitly used as the node's ID, and distance computations among nodes
can be done in ID space without requiring physical measurements.

@@

One major limitation of \textit{Mithos} is that the protocol cannot handle
dynamic arrivals and departures from the network, as is happens in mobile
networks.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing comunication latency among peers but its
% efficience is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used througout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incrimental probing is applied in quadradants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It minimises routing length, but may suffer load imbalance since nodes higher
% in the tree hierarchy are more likely to route most of the messages in the
% overlay.
medium &
% Heartbeat approach incurs extra control overhead to the network. Fortunatelly
% involves only the parent and the children of the departing/failing node.
% nodes.
low &
% Seems to scale nicely from 10K- to 1M-node testbeds.
high
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
medium &
% 
medium &
%
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Simple approach that exploits proximity but it is coarse grained and thus not
% efficient.
low &
%
low &
%
medium
\end{tabular}
\end{center}

@@

%
% TODO: SOME DISCUSSION
%
%The use of Traceroute as a tool for implementing the distance measuring
%infrastructure raise concearns about its efficiency and scalability. Being,
%primarilly, a network diagnostic utility,
% Even though traceroute provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% traceroute is a very heavy tool and thus incurs excessive burden to the
% network resourses.
high &
% Traceroute is categorised as too heavy-weighted and intrucive for use in a
% larger scale system \cite{ratnasamy_binning_2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PChord}
\emph{PChord}\cite{hong_pchord_2005} is a based on the Chord DHT which adds
proximity routing into its routing mechanism. The main modification over the
vanilla Chord is the inclusion of a \emph{proximity list} into its routing table
so that the next hop is decided based not only by considering best progress
towards the key, but on the physical proximity of the candidate nodes as well.
The list is, at join time, empty but as the PChord node starts to interact with
other nodes it applies a heuristic mechanism to fill up the list. Entries are
dynamicaly added or removed as the network state changes. The overlay
maintenance cost can be considered similar to Chord's since besides node
join/leave and cost of finger table entries heartbeat, PChord adds heartbeat of
nodes inside the proximity list but since this list always contains nodes with
the lowest RTT the added cost is kept to a minimal.

Due to the fact that, with each step, there is always progress towards the
target node in the ID space, PChord will result in a reduced hop number than
Chord, since each hop in PChord is larger or at least equal in the key space.
Passing through proximity links in the underlaying network means reduced routing
cost. Additionally, if the number of entries in the proximity list is the same
as the number of network partitions, PChord prevents hops from jumping in and
out the network partition the current node belongs to.

% TODO: SOME DISCUSSION
% TODO: NEEDS REWORDING
% PChord’s main routing optimizations are of less overlay hops, passing
% proximity links of the underly network and passing the same network partition
% only once in the routing path, which directly results in the lower RDP of
% routing efficiency. Meanwhile, PChord keeps light-weightmaintenance cost as
% Chord does.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Small decrease in needed overlay hops per object publishing
medium &
% The are heartbeat mechanism for both finger table and proximity list adds a
% burden to the network by default. But the overall overhead is decreased as
% the proximity list becomes longer.
medium &
% Improvement of routing is achieved with more object pointers helping to
% shorten the routing path of object querying. When the distance of query source
% to target is far away both Chord and PChord achieve the average hop number to
% not increase.
high
\end{tabular}
\end{center}

@@

% TODO: MAYBE REVIEW THE EVALUATION
\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% good routing efficiency
medium &
% Releaves the system from joining overhead and topology aware ID construction
% but doubles the information needed to be stored and maintained by the
% introduction of neighbouring table
medium &
% assumes the operation of ideal underlying anycast mechanism (meaning that
% outside messages are always routed to the nearest node which in the current
% Internet, this is not always feasible. Moreover, is designed on the basis of
% IPv6 protocol which is not widely operational yet.
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Chord6}
\emph{Chord6} \cite{xiong_chord6_2005} is another Chord variant that tries to
exploit the hierarchical features of IPv6 in order to create a substrate that
reduces inter-domain traffic between service providers. The difference between
Chord6 and Chord the identifier definition. Therefore, the approach can be
easily portable to other DHTs such as CAN, Pastry and Tapestry. In Chord6 the
identifier contains two parts: the higher bits are obtained by hashing the
node's IPv6 address prefix of specific length, while the remaining lower bits
are the hash value of the rest of that IPv6 address. As a result of this
assignment, nodes in a domain will be mapped onto a continuous key space on the
overlay network, which avoids unnecessary message forwarding across different
service providers, thus minimising overall routing cost.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Can reduce intra-domain average path length but even though nodes in the same
% domain would have close identifiers, nodes in two close domains may have very
% different ones reducing the overal efficience of the approach in general when
% considering inter-domain average path length.
low &
% The construction of the identifier space is done at node join and in an
% independent fashion involving the application of two hash functions meaning
% resulting in low overhead stress to the network and its nodes.
low &
% Is designed on the basis of IPv6 protocol which is not widely operational yet.
medium
\end{tabular}
\end{center}

@@

% TODO: MAYBE REVIEW THE EVALUATION
\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
%
medium &
%
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-Chord}
The approach that is proposed by Sun and Zhang in \cite{sun_quasi_2008}, tries
to address the topology mismatch problem, at the construction phase of the
Chord identifier cycle, on the the basis of underlying topology information.
The proposed model constructs the \emph{Quasi-Chord} ovelay network in three
steps. First, each host acquires its coordinates in the geometric space
utilizing the \emph{global network position (GNP)} protocol \cite{ng_gnp_2001}.
Second, using the \emph{Cantor space filling curve}, the $2$-dimensional space
is converted to a $1$-dimensional one, used in the last, third, step to build
the Quasi-Chord circle according to the host's Cantor value. In Quasi-Chord
each node stores 2 finger tables; one clockwise and one counter-clockwise.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The algorithm shows to reduce end-to-end delay as well as not produce
% duplicates of messages.
medium &
% The overhead is more compared to vanilla chord since mapping of 2-dimensional
% space to 1-demensional with Cantor SPF adds some extra burden in time
% complexity. Also the addition of the couter-clockwise finger table doubles the
% data, per se, needed to be stored and maintained.
high &
% The GNP system is a static landmark approach making things not fully
% distributed and thus constrain the model's scalability.
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of proximity detection through the prefix matching technique
% is caught in a vicious cycle with the storage space needed for DHT object
% publishing (how many bits will be used for either)
low &
% The overhead for detecting proximity is only comparison of prefixes
low &
%
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The result of experiments show that the Cone, compared with Chord, has obvious
% improved on the delay of route and the hops of overlay networks…
medium &
% The approach incorporates a static landmark + RTT to these landmarks in order
% to exploit proximity information thus incurring low overall additional
% operational overhead but imposing extra stress to the landmarks themselves 
medium &
% landmark based approaches are not full distributed thus not smoothly scalable.
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% The paper suggests that this approach generates significantly lower overhead
% than the vanilla Pastry algorithm
low &
% Dynamic landmarkin approach helps the scalability of the algotithm. The
% authors claim that the temporary nature of RLM's landmark nodes does not
% prevent them to maintain a good ratio in the presence of high landmark
% degression rates.
high
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% SAT-Match seems to outperform landmark binning in the sense of providing a
% higher grained differenciation of proximity, adding to the fact that
% SAT-match is fully distributed. Also to further enhance the efficiency it can
% work cooperatively with landmark binning itself.
high &
% distance probing and iterative computations add to the approach's overhead.
% Also the fact that the selective jumps are not always performed the added
% overhead to efficiency gained is not guarranteed in any configuration and
% circumstance.
medium &
% The self-adaptation nature of the algorithm and the selective jump mechanisms
% scale much better than, for example, Mithos.
medium
\end{tabular}
\end{center}

@@

% TODO: MAYBE REVIEW THE EVALUATION
\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
low &
%
low &
%
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion on the Algorithms for Structured Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Structured P2P network algorithms use a global distributed hash table or a
prefix tree structure to uniquely lookup peers or their data in the overlay
network. As all the data is kept within the overlay, each node behaves as a
client and a server, therefore nodes join and leave according to rules
determined by the integrity of the global data structure. The main advantage of
the structured P2P topology is that by the help of the global data structure,
peers or their data can be found within the network even if there is only a
single copy of that item present. However, each node join and leave creates
maintenance overhead for the network due to updates required by the global data
structure, and for networks with frequent node arrivals and departures the
topology uses valuable network resources just to update the global structure.
Nodes join the network by using a key value, which determines the location and
the neighbourhood of the new node within the network. However, assigning
random key values to the newly inserted nodes creates non-optimal matching with
the underlying physical network topology, therefore, increasing the overhead of
the network even more. One solution for handling the topology mismatch problem
is to consider the proximity of the peers when generating the key and joining
the node to the network, so that nodes within the same network domains are
selected as peers, or neighbours, during the overlay topology construction.

This section gathered together some of the most distinctive research work that
can be found in the literature for addressing the inefficient network resource
utilisation in structured architectures imposed by the topology mismatch
problem. A categorisation of the methods used for achieving their goals is the
following based on previous work from
\cite{castro_proximitydht_2002,castro_topawareroute_2002,ratnasamy_openq_2002}:
\begin{inparaenum}[\itshape i\upshape)]
  \item geographic-layout-based,
  \item proximity-routing-based,
  \item proximity neighbour selection based,
\end{inparaenum}

A quick overview can be obtained in Table~\ref{structured:table}. Topology
adaptation, landmarking and caching/replication have been visited during the
discussion on unstructured systems in Section~\ref{section:unstructured} so
we will not elaborate more here. Again, we additionaly gather highlights and a
rough estimation of each algorithm's positive and negative aspects regarding
their implementation.

\input{structured-table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Geographic layout} \label{section:geographic_layout}
Inside geographic layout category fall those kind of methods which practically
position physically close by nodes together in the application space as well.
This is done by adjusting and maintaining the routing tables of all involved
peers accordingly by exploiting proximity information that describe the overall
geographic positioning of the peer nodes. Landmark servers and RTT measurements
are two popular methods, which can also be used in conjunction, to discover
physically close by peers over the network. However, as discussed in Section
\ref{sec:landmark_binning}, these methods do not always give reliable estimates
for the node positions over the internet. The landmark servers are not
self-organizing and have maintenance overheads. To serve a P2P network with
millions of peers, multiple landmark servers distributed over the whole world is
required, which is hard to manage. The RTT measurements also can measure the
delay between peers, but it is a greedy method, which can result non-optimal
overlay topologies especially if close by nodes have low bandwidth connections
among themselves.

Even though managing the overlay structure based on the geographic layout of the
nodes improves the query efficiency of the system, on the other hand, it tends
to create hotspots, and the needed failure resilience is undermined by the fact
that close by nodes are more likely to suffer collective failures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: Geographic Layout
%
%\begin{itemize}
% \item Geographic Layout\\
%The node IDs are assigned in such a way that nodes close by in the physical
%network topology, be close in the node ID space as well. Implementations that
%work relatively well with this approach have been incorporated into CAN. Nodes
%measure the RTT between themselves and a set of landmarks in order to match the
%CAN space as much as possible to the physical one. Unfortunately, the approach
%requires well known landmark servers and for that matter is  not fully
%self-organizing which can further lead to imbalanced node distribution. On
%other DHTs, such as Chord or Pastry, another problem emerges.  To gain fault
%tolerant properties, these protocols, replicate key-value pairs on neighbouring
%(in the ID space) nodes. When a proximity-based node ID assignment has been
%used, the needed failure resilience is undermined by the fact that close by
%nodes are more likely to suffer collective failures.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Proximity Routing}
Proximity routing does not require routing tables to be built using any
knowledge about network proximity. On the other hand it exploits such knowledge
in order to choose the best next hop during routing a message. This approach
tries to balance between choosing the node that will further progress the
routing towards the destination and choosing the closest entry in the routing
table, in terms of network proximity. As this is very difficult to be achieved,
the system might end up using a greedy approach that selects low latency paths
over the overlay, which maps to suboptimal longer paths on the physical
topology. Thus, in general, proximity neighbour selection is considered as a
superior method to proximity routing, however, joint uses of these two protocols
are also possible. Moreover, they are considered relatively less effective than
geographical layout when applied to CAN(-like) implementations. Moreover, the
technique has been incorporated into a version of Chord causing an increase on
the overhead of node joins and the size as well as maintenance cost of finger
tables.

%
%\cite{dabek_cfs_2001} proposes a server selection scheme for the Chord DHT, on
%the domain of proximity routing selection. In \emph{CFS}, each node predicts
%the entire lookup latency as a function of the total number of nodes and the
%average overlay next routing peer. The problem is that it is very difficult to
%have a clear picture on the total number of nodes and the average hop latency
%from the local. This leads to rough estimations that consequently decreases
%overall performance.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Proximity neighbour selection}
\emph{Proximity Neighbour Selection} constructs the routing tables using
proximity knowledge. The proximity information used in this method is different
than the landmark based systems described in
Section~\ref{section:geographic_layout}, as time-to-live values between nodes,
or directly node ID prefixes are used to detect proximity. Tapestry, Pastry, and
CAN successfully implemented the proximity into their algorithms by using this
approach. The routing protocol in Pastry is based on longest node ID prefix
matching, while CAN uses RTT values to detect close by nodes.
\cite{castro_proximityp2p_2002} reports that proximity neighbour selection as an
effective proximity based method.
